---
title: 'Class 6: Writing your own R functions'
author: "Aries Chavira"
date: "1/24/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lesson 1 

1. lets insert a code chunk with the shortcut `option-CMD-i`:

2. read.table(file, header = TRUE, sep = "\t") == read.delim 
    This is beacuse **read.table()** is the parent funciton of 
    - read.csv
    - read.csv2
    - read.delim
    
## Saving Files 
Table one 

```{r}
x <- read.table("test1.txt", sep = ",", header = TRUE)
x
```

Table two
```{r}
x <- read.table("test2.txt", sep = "$", header = TRUE)
x
```

Table three
```{r}
x <- read.table("test3.txt")
x
```

## Lesson two 

#Creating Functions 

This is an example of a function named `add` with input `x` and `y`.
```{r}
add <- function(x, y=1) {
  # Sum the inputs x, and y
  x + y
}
```

Try using it! 

Example 1: 
```{r}
add(x=c(1,6,2), y=4)
```

Example 2:
```{r}
x <- c(10,4,22,6)
min(x)
max(x)
range(x)
```

Example 3: 
```{r}
rescale <- function(x) {
  rng <- range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng)
}
```

```{r}
x <- c(10,4,5,3,12,NA)
rescale(x) 
```

Rescale 3
```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {

    rng <-range(x, na.rm=na.rm)
    print("Hello")
 
    answer <- (x - rng[1]) / (rng[2] - rng[1])
    
    if(plot) {
      plot(answer, typ="b", lwd=4)
    }
  print("is it me you are looking for?")
  print("I can see it in ...")
}

rescale3(x)
```

## Working with bio3d package

To use funcitons for any package type `library()` to load it. 
```{r}
library("bio3d")
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

what is read.pdb?
```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s1
```

```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
points(s2.b, col="blue", type="l")
points(s3.b, col="red", type="l", lwd=3)
```



