---
title: 'Class13: Drug Discovery'
author: "Aries Chavira"
date: "2/19/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Retrieve and process starting HIV protease structure 

Here we download and clean the HIV-Pr structure (pdb codeL 1HSG) from PDB database. We will separate the "protein-only" and "ligand only" into two PDB files  

```{r}
library(bio3d)
```

```{r}
file.name <- get.pdb("1HSG") 
```

We will use `read.pdb`, `atom.select`, and `write.pdb` functions to make our seperate "Protein-only" and "Ligand only" PDB files 

```{r}
HIV <- read.pdb("1HSG")

HIV
```
```{r}
Protein <- atom.select(HIV, "protein", value = TRUE)

Ligand <- atom.select(HIV, "ligand", value = TRUE)
```
 
 
```{r}
prot.pdb <- write.pdb(Protein, file = "1hsg_protein.pdb")

lig.pdb <- write.pdb(Ligand, file = "1hsg_ligand.pdb")
```

## Reading docking results 

converting results into a .pdb instead of .pdbqt
```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```






