---
title: "Class17"
author: "Aries Chavira"
date: "3/4/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```

Questions to answer 
 1. How many total infected cases are there 
 2. How many deaths linked to infection have there been 
 3. What is the overall death rate of the disease of the entire dataset 
 4. What is the death rate in China respectively 
 5. What is the death rate in Italy, US, and Iran? 
 
 1. How many total infected cases are there 
```{r}
total_cases <- sum(virus$cases)
```
 
2. How many deaths linked to infection have there been 
```{r}
death <- virus$type=="death"
death_cases <- sum(virus[death,"cases"])
```

 3. What is the overall death rate of the disease of the entire dataset 
```{r}
3160/144233 *100
```

4. What is the death rate in China respectively 
```{r}
main_china <- virus$Country.Region=="Mainland China"
main_china <- virus[main_china, ]
main_china
```

```{r}
china_dead <- main_china$type=="death"
dr_china <- sum(main_china[china_dead, "cases"])
dr_china 
```
```{r}
total_china <- sum(main_china$cases)
china_death_rate <- dr_china / total_china * 100
china_death_rate
```

ITALY 
```{r}
italy <- virus$Country.Region=="Italy"
total_italy <- virus[italy, ]
total_italy
```

```{r}
italy_deaths <- total_italy$type=="death"
dr_italy <- sum(total_italy[italy_deaths, "cases"])

total_infected_italy <- sum(total_italy$cases)
italy_death_rate <- dr_italy/ total_infected_italy * 100
italy_death_rate

```

```{r}

```













