---
title: "Class17: Corona virus investigation"
author: "Aries Chavira"
date: "3/4/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```

Questions to answer 
 1. How many total infected cases are there 
 2. How many deaths linked to infection have there been 
 3. What is the overall death rate of the disease of the entire dataset 
 4. What is the death rate in China respectively 
 5. What is the death rate in Italy, US, and Iran? 
 
 1. How many total infected cases are there 
```{r}
total_cases <- sum(virus$cases)
```
 
2. How many deaths linked to infection have there been 
```{r}
death <- virus$type=="death"
death_cases <- sum(virus[death,"cases"])
```

 3. What is the overall death rate of the disease of the entire dataset 
```{r}
3160/144233 *100
```

4. What is the death rate in China respectively 
```{r}
main_china <- virus$Country.Region=="Mainland China"
main_china <- virus[main_china, ]

china_dead <- main_china$type=="death"
dr_china <- sum(main_china[china_dead, "cases"])
dr_china 

total_china <- sum(main_china$cases)
dr_in_china <- dr_china / total_china * 100
dr_in_china
```

> Death rate in ITALY 

```{r}
italy <- virus$Country.Region=="Italy"
total_italy <- virus[italy, ]

italy_deaths <- total_italy$type=="death"
dr_italy <- sum(total_italy[italy_deaths, "cases"])
dr_italy

total_infected_italy <- sum(total_italy$cases)
dr_in_italy <- dr_italy/ total_infected_italy * 100
dr_in_italy
```

> Death rate in IRAN

```{r}
iran <- virus$Country.Region=="Iran"
only_iran <- virus[iran, ]

iran_dead <- only_iran$type=="death"
dr_iran <- sum(only_iran[iran_dead, "cases"])
dr_iran

total_infected_iran <- sum(only_iran$cases)
dr_in_iran <- (dr_iran / total_infected_iran * 100)
dr_in_iran
```

> Death rate in the US 

```{r}
us <- virus$Country.Region=="US"
total_us <- virus[us, ]

us_deaths <- total_us$type=="death"
dr_us <- sum(total_us[us_deaths, "cases"])
dr_us

cases_us <- sum(total_us$cases)
cases_us

dr_in_us <- (dr_us / cases_us * 100)
dr_in_us
```

```{r}
dr_china
dr_italy
dr_iran

dr_in_china
dr_in_iran
dr_in_italy
dr_in_us

```

```{r}
US <- virus$Country.Region=="US"
today_us <- virus[US, ]

sum()
```


```{r}
library(dplyr)

cases_by_country <- virus %>%
    group_by(Country.Region) %>%
    summarise(tot=sum(cases)) %>% 
    arrange(desc(tot))

cases_by_country
```









