---
title: "Unsupervised learning"
author: "Aries Chavira"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up

## Get our input data

Our data for today come from the Wisconsin Breast Cancer Diagnostic Data Set

```{r}
wisc.df <- read.csv("WisconsinCancer.csv")
head(wisc.df)
```

```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```

> Q. How many patients are there in this dataset?

```{r}
nrow(wisc.df)
```

> Q. How many cancer and non-cancer patients are there?

```{r}
table(wisc.df$diagnosis)
```

```{r}
sum(wisc.df$diagnosis == "M")
```

> Q. How many cols are "_mean" values?

```{r}
colnames(wisc.df)
```

We can use the `grep()` function to see this

```{r}
grep("_mean", colnames(wisc.df), value=TRUE )
```

We can take the `length()` of this to find how many matches there are
```{r}
length( grep("_mean", colnames(wisc.df)) )
```


## Enter Principal Component Analysis

First we need to check whether our input data should be scaled. Lets check the sd() and mean() of all our columns in `wisc.data`

```{r}
wisc.pr <- prcomp( wisc.data, scale=TRUE )
summary(wisc.pr)
```

```{r}
attributes(wisc.pr)
```

We want the `X` component to make our PCA plot 

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
```
```{r}
data.scaled <- scale(wisc.data)

data.dist <- dist(data.scaled)

hc <- hclust( dist(wisc.data) ) 
plot(hc)

```
There doesnt seeem to be a good place to cut the tree, so... ; 

## Cluster in PC space 

Use the results of PCA to do my clustering 
```{r}
wisc.pr.hc <- hclust( dist(wisc.pr$x[,1:3]), method="ward.D2" )
plot(wisc.pr.hc)
```
```{r}
grps <- cutree(wisc.pr.hc, k=2)
table(grps)
table(grps, wisc.df$diagnosis)
```
```{r}
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
npc

plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
points(npc[,1], npc[,2], col="coral", pch=16, cex=3)
text(npc[,1], npc[,2], labels=c(1,2) , col="white")
```











